Model

### 2019-04-22 stats/model.Rmd
more iterations

# sem_know_model<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
# )
# 
# saveRDS(sem_know_model, "../saves/sem_know_model.rds")

#sem_know_model <- readRDS("../saves/sem_know_model.rds")

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH", 
                        samples = 5000, 
                        burn = 2500,
                        verbose = T,
                        verboseLag = 500)
)

@@

# sem_know <- sem_know_model %>%
#   select(value) %>%
#   map_df(bind_rows)%>%
#   rename(sem_int = `0.sem_int`,
#          sem_slope = `0.sem_slope`,
#          familiar = `0.familiar`,
#          so_int = `0.so_int`,
#          so_slope = `0.so_slope`)%>% 
#   gather(parameter, value, -familiar)

>>>>

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH", 
                        samples = 10000, 
                        burn = 2500,
                        verbose = T,
                        verboseLag = 500)
)

@@
